### 2023-06-16 manuscript.tex
Responded to Paul's comments. Some new text and citations. [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/39b67330882bd6a00851c8595baf225d32892b11.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/39b67330882bd6a00851c8595baf225d32892b11/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5291552036

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/192b16d94263109406c3457018cf55bec4a36281/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/192b16d94263109406c3457018cf55bec4a36281}{stain/2022-fdo-paper@192b16d}
on June 16, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/39b67330882bd6a00851c8595baf225d32892b11/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/39b67330882bd6a00851c8595baf225d32892b11}{stain/2022-fdo-paper@39b6733}
on June 16, 2023.
